MSAD_PCA_Walkthrough

### 2017-01-10 Simulation_Vignette.Rmd
More vignette edits

# plot(normal_df$t)
# plot(normal_df$x)
# plot(normal_df$y)
# plot(normal_df$z)
# scatterplot3d(x = normal_df$x,
#               y = normal_df$y,
#               z = normal_df$x)
# # It checks out

orig_state_mat <- normal_df %>% select(x,y,z) %>% as.matrix
```

Now we can create data for our other two states. These states will be scaled rotations of the current $<x,y,z>$ set. Thus, we need the `rot_and_scale3d()` function from the `Rotation_Playground.R` file.

```{r state_2_init}
source("inst/Rotation_Playground.R")

###  State 2  ###
state2_angles <- list(yaw = 0,
                      pitch = 90,
                      roll = 30)
state2_scales <- c(1,0.5,2)
state2_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                               scale_factors = state2_scales)
scatterplot3d(state2_mat)

###  State 3  ###
state3_angles <- list(yaw = 90,
                      pitch = 0,
                      roll = -30)
state3_scales <- c(0.25,0.1,0.75)
state3_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                               scale_factors = state3_scales)
scatterplot3d(state3_mat)

###  Combination and Cleaning  ###
# Now concatenate these vectors
normal_df$xState2 <- state2_mat[,1]
normal_df$yState2 <- state2_mat[,2]
normal_df$zState2 <- state2_mat[,3]
normal_df$xState3 <- state3_mat[,1]
normal_df$yState3 <- state3_mat[,2]
normal_df$zState3 <- state3_mat[,3]

@@

###  Hourly Switching Process  ###
state1_df <- normal_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
state2_df <- normal_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
state3_df <- normal_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
normal_switch_df <- bind_rows(state1_df, state2_df, state3_df) %>%
  arrange(dateTime)

>>>>

# plot(normal_df$t)
# plot(normal_df$x)
# plot(normal_df$y)
# plot(normal_df$z)
# # It checks out

orig_state_mat <- normal_df %>% select(x,y,z) %>% as.matrix
```
Let's take a look at our 3D scatterplot:
```{r state1_scatter}
scatterplot3d(x = normal_df$x,
              y = normal_df$y,
              z = normal_df$x)
```

Now we can create data for our other two states. These states will be scaled rotations of the current $<x,y,z>$ set. Thus, we need the `rot_and_scale3d()` function from the `Rotation_Playground.R` file. The first state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2).
```{r state_2_init}
source("inst/Rotation_Playground.R")

###  State 2  ###
state2_angles <- list(yaw = 0,
                      pitch = 90,
                      roll = 30)
state2_scales <- c(1,0.5,2)
state2_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                               scale_factors = state2_scales)
```
We can see the effects of the rotation and scaling.
```{r state_2_scatter}
scatterplot3d(state2_mat)
```
The second state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
```{r state_3_init}
###  State 3  ###
state3_angles <- list(yaw = 90,
                      pitch = 0,
                      roll = -30)
state3_scales <- c(0.25,0.1,0.75)
state3_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                               scale_factors = state3_scales)
```
We can see the difference that State 3 creates.
```{r state_3_scatter}
scatterplot3d(state3_mat)
```

Now, let's combine all these state observations into one data frame, which we will then subset based on the state indicator.
```{r combine_state_data}
###  Combination and Cleaning  ###
# Now concatenate these vectors
normal_df$xState2 <- state2_mat[,1]
normal_df$yState2 <- state2_mat[,2]
normal_df$zState2 <- state2_mat[,3]
normal_df$xState3 <- state3_mat[,1]
normal_df$yState3 <- state3_mat[,2]
normal_df$zState3 <- state3_mat[,3]

@@

###  Hourly Switching Process  ###
state1_df <- normal_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
state2_df <- normal_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
state3_df <- normal_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
normal_switch_df <- bind_rows(state1_df, state2_df, state3_df) %>%
  arrange(dateTime)
```

Let's take 
```{r}
